#The data is from “data_cleanedup” by Thomas and “FCMStress_gamm” by Ziqi. Both forms are applicable
#GAMM   Closer to the true hypothesis
# Building the GAMM Model

```{r}
gamm_model <- gamm(
  ng_g ~ s(TimeDiff) + s(Distance) + s(between_time),
  random = list(Sender.ID = ~1),       # Random effects: individual differences
  data = merged_data,
  family = Gamma(link = "log")         # Gamma distribution, log link
)
```


#GAMM  Lower complexity, better fit
```{r}
gamm_model <- gamm(
  ng_g ~ s(TimeDiff) + s(Distance) + s(between_time),
  random = list(Sender.ID = ~1),      
  data = merged_data,
  family = Gamma(link = "identity")         #  Gamma distribution, identity link
)
```


#GLMM Easy to understand but difficult to capture nonlinear relationships
```{r}
glmm_model <- glmer(
  ng_g ~ TimeDiff + Distance + (1 | Sender.ID),  # Fixed and random effects
  data = data_gamm,
  family = Gamma(link = "log")                
)
```


#random forest model  More robust to outliers and missing values.
```{r}
rf_model <- randomForest(
  ng_g ~ TimeDiff + Distance + between_time,
  data = merged_data,
  ntree = 500,
  importance = TRUE
)
importance(rf_model)
```


#Due to the complexity of the data, we believe that time series models(GAMM-AR or ARIMA) and neural networks are also worth trying.

